Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2018-10-21 pkg/disttree/inst/draft/draft.Rnw
adaption to new results of Rain_distribution and further revisions based on reviews
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2347 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: bd7c6bbd46a5fc06879c99fb98375489d745a676

\item \emph{Distributional forest:} All 80~predictor variables are
  considered for learning a forest of 100 trees. Subsampling is employed 
  for each tree using a third of the predictors
  in each split of the tree (\code{mtry}). Parameters are estimated by
  adaptive local likelihood based on the forest weights as described
  in Section~\ref{sec:methods}. 
  \hlc{As stopping criteria the minimal number of observations to perform a split} 
  (\code{minsplit}) \hlc{is set to $50$, the minimal number of observations in a 
  terminal node} (\code{minbucket}) \hlc{is set to $20$ and the significance level 
  for variable selection} (\code{alpha}) \hlc{is kept at the default value $1$ such 
  that no early-stopping (sometimes also refered to as ``pre-pruning'') is applied
  based on results of the statistical tests.}
  % stopping criteria:
  % forest_minsplit = 50, forest_minbucket = 20, forest_mincrit = 0

@@

Alternatively, a distribution including an addidtional parameter capturing skewness
\citep{Scheuerer+Hamill:2015, Baran+Nemoda:2016} could be applied. For example, 
in transformation forests} \citep{Hothorn+Zeileis:2017} \hlc{a very flexible 
five-parametric distribution family is employed such that skewness can be modeled 
explicitly.
Evaluating further distributions might be of interest but this would go beyond the
scope of this manuscript.
}

>>>>

\item \emph{Distributional forest:} All 80~predictor variables are
  considered for learning a forest of 100 trees. Subsampling is employed 
  for each tree using a third of the predictors
  in each split of the tree (\code{mtry}). Parameters are estimated by
  adaptive local likelihood based on the forest weights as described
  in Section~\ref{sec:methods}. 
  \hlc{As stopping criteria the minimal number of observations to perform a split} 
  (\code{minsplit}) \hlc{is set to $50$, the minimal number of observations in a 
  terminal node} (\code{minbucket}) \hlc{is set to $20$ and the significance level 
  for variable selection} (\code{alpha}) \hlc{is kept at the default value $1$ such 
  that no early-stopping (sometimes also referred to as ``pre-pruning'') is applied
  based on results of the statistical tests.}
  % stopping criteria:
  % forest_minsplit = 50, forest_minbucket = 20, forest_mincrit = 0

@@

Alternatively, a distribution including an additional parameter capturing skewness
\citep{Scheuerer+Hamill:2015, Baran+Nemoda:2016} could be applied. For example, 
in transformation forests} \citep{Hothorn+Zeileis:2017} \hlc{a very flexible 
five-parametric distribution family is employed such that skewness can be modeled 
explicitly.
Evaluating further distributions might be of interest but this would go beyond the
scope of this manuscript.
}

### 2018-10-21 pkg/disttree/inst/draft/rejoinder.Rnw
adaption to new results of Rain_distribution and further revisions based on reviews
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2347 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: bd7c6bbd46a5fc06879c99fb98375489d745a676

For each new observation $z$ the corresponding 
parameter vector $\hat{\Theta}(z)$ can be calculated following 
the given formula. But you are right, this is equivalent to simply
obtaining the paramter vector that has been estimated in the 
corresponding node when learning the tree. This is now also
explained at the end of Section~2.2.

@@

Yes, significance can be used as one of the stopping criteria,
so that partitioning is stopped early upon non-signifcance
of the tests. This is sometimes also called ``pre-pruning'' in
the tree literature.

>>>>

For each new observation $z$ the corresponding 
parameter vector $\hat{\Theta}(z)$ can be calculated following 
the given formula. But you are right, this is equivalent to simply
obtaining the parameter vector that has been estimated in the 
corresponding node when learning the tree. This is now also
explained at the end of Section~2.2.

@@

Yes, significance can be used as one of the stopping criteria,
so that partitioning is stopped early upon non-significance
of the tests. This is sometimes also called ``pre-pruning'' in
the tree literature.
